Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-08 paper/paper.tex
pass on some sections

\section{Differential Testing Infrastructure}
\label{sec:design}

%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
\begin{figure}[h]
  \centering
%  \includegraphics[trim=20 350 200
%    0,clip,width=0.35\textwidth]{google-awards-workflow}
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
\end{figure}

@@

@@

The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
false and true positives observed with test transplantation. The top
piechart shows false alarms.  It is important to stress that all the
``transplanted'' tests should have passed in these cases. The absolute
number of tests in each category is shown in parentheses to the
right-side of the label of a slice, nameing the source of false
positive. The sources are as follows:

@@

  \item \textbf{Unknown.} This category corresponds to the cases we
    were unable to confidently diagnose the failure.  \Igor{ We
      observed that some tests are not valid due not corresponds to
      the ES6 specifications, we skip these warnings.  }\Mar{Igor,
      this is not well-formed english and I don't understand what you
      want to say.}

@@

In summary, we observed that \Fix{...elaborate...}

Considering true positives, \Fix{...elaborate...}

@@

Figure~\ref{tab:test-transplantation-bugs} shows
results. \Fix{...elaborate...}

\Igor{
  JSC Severity doc \url{https://webkit.org/bug-prioritization/}
  Chakra usa label para definir prioridades, porem neste doc nao ha explicacao das severidades
  \url{https://github.com/Microsoft/ChakraCore/wiki/Label-Glossary}. Contudo, se clicar nessas 
  labels vai direcionar para as issues e la pode-se ver a severidade de cada.
  V8 guidelines \url{https://www.chromium.org/for-testers/bug-reporting-guidelines/chromium-bug-labels}
}

@@

>>>>

@@

\subsubsection{Differential Testing Infrastructure}
\label{sec:design}

%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
\begin{figure}[t!]
  \centering
%  \includegraphics[trim=20 350 200
%    0,clip,width=0.35\textwidth]{google-awards-workflow}
  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
\end{figure}

@@

The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
false and true positives observed with test transplantation. The top
piechart shows false alarms, which means that all
``transplanted'' tests should have passed in these cases. The absolute
number of tests in each category is shown in parentheses to the
right-side of each slice label, naming the source of false
positive. The sources are as follows:

@@

  \item \textbf{Unknown.} This category corresponds to the cases we
    were unable to confidently diagnose the failure.

@@

We observed that the sources of false positives were relatively
uniformly distributed, with the categories ``Unknown'' and
``Undefined'' holding more representation with \Fix{X and Y} reports,
respectively. Considering the true positives, we found a reasonable
number of duplicate reports, but not enough high to justify attempting
to automate the detection of duplicates. Section~\ref{sec:bugs}
exemplifies cases of false and true positives.

@@

@@

Figure~\ref{tab:test-transplantation-bugs} lists all bugs we found
with test transplantation. The first column shows the identifier we
assigned to the bug, column ``Date'' shows the date the bug was
reported in the format ``m/dd'', column ``Engine'' shows the affected
engine, column ``Status'' indicates the status of the bug report at
the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
''Fixed''), column ``Url'' shows the web address for the corresponding
post in the bug tracking system where the discussion thread with
engine developers can be found (de-anonymized upon request), column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test. Considering severity levels, it is important to note that
\jsc{} uses five different severity levels~\cite{jsc-severity} whereas
Chakra~\cite{chakra-severity} and \smonkey{}~\cite{mozilla-severity}
use only two. As usual, the smallest the severity value the highest
the severity of the bug. We use a dash (``-'') as the severity level
for bugs with pending confirmation.

Of the \Fix{17} bugs we reported with test transplantation, \Fix{9}
were analyzed and moved from the status ``New'' to ``Confirmed''
(\ie{}, no bug we reported was rejected). Of these, \Fix{8} of them
are severity-2 bugs.  \chakra{} was the engine with the highest number
of confirmed bugs, \Fix{8} in total, with \Fix{1} bug
fixed. Considering the remaining engines, \veight{} confirmed one
bug. Curiously, Google engineers confirmed that report in a few
hours. Athough we did not find any showstopper critical bugs, most of
the bugs are seemingly important as per the categorization given by
engineers. Analyzing the issue tracker of \chakra, we found that
severity-1 bugs are rare.
